Multisensor Architecture for an Intersection Management System

### 2015-03-22 ch2-mdf_ims.tex
Some corrections and parragraph added to ch2. conclusions

%\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}

@@

Several models, architectures and frameworks have been proposed in literature; some of them to show how a data fusion system should work and some other providing guidelines on how to implement it in a given application.

>>>>

%\begin{document}

\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}

@@

Several models, architectures and frameworks have been proposed in literature; some of them to show how a data fusion system should work and some other providing guidelines on how to implement it in a given application. Also, a wide range of algorithms have been used to perform fusion of data, some classified by the nature of the fusion or by the nature of the data, but is finally the environment and the application itself which determines the approach to use.

%\end{document}
